\section{Details of the ZeroBias dataset}
\label{sec:zerobias}

Data events are collected via the \texttt{ZeroBias} stream. This stream replaces the \texttt{MinBias} stream in 2015 data-taking as the recommended source of unbiased proton collisions. Another usage of the stream is to provide data events used in MC overlay of additional pileup interactions. 

The stream triggers on ``zero bias'' events by acknowledging a L1 \texttt{EM15} trigger and recording the event one LHC orbit after this. This ensures the recorded event is from a filled bunch crossing but makes no further requirements of the event.

The stream is pre-scaled to 10 Hz throughout 2015. 5 Hz of triggers are allocated for inclusive zero bias events, \texttt{HLT\_noalg\_zb\_L1ZB}, and 5 Hz of triggers are allocated for zero bias events where additionally a jet is required at HLT with $\pt > 40$ GeV, \texttt{HLT\_j40\_L1ZB}. Both triggers are seeded by \texttt{L1\_ZB}. More details on the stream are available at the \href{https://twiki.cern.ch/twiki/bin/viewauth/Atlas/Run2StreamingSetup}{Run2StreamingSetup twiki}.

Data events are required to be in lumi blocks where all detector and reconstruction elements are reported to be functioning properly, which are collected in a good runs list (GRL). Exceptionally, Run 281143 is included in the GRL, when the insertable $b$-layer (IBL) was turned off. The absence of the IBL does not affect the \texttt{ZeroBias} triggers or the operation of the MDT and CSC. The GRL used here is:

\texttt{data15\_13TeV.periodAllYear\_DetStatus-v73-pro19-08\_DQDefects-00-01-02} \\
\texttt{\_PHYS\_StandardGRL\_All\_Good\_25ns\_tolerable\_IBLSTANDBY-DISABLE.xml}

Because the study is not statistically limited, not all events are used in the study. A random sample of 10-50\% of each run is used in the studies. The runs are described in more detail in Table~\ref{tab:zerobias}.

\begin{table}
  \begin{center}
    \begin{tabular}{c|c|c|c}
      Run    & Int. lumi. [\ipb] & Bunches & Events used \\
      \hline
      278880 &             22.7  &     447 & 51304 \\
      279169 &             57.8  &     733 & 70949 \\
      279345 &             54.9  &     877 & 53972 \\
      279685 &             78.2  &    1021 & 57115 \\
      280231 &             93.2  &    1165 & 51597 \\
      280464 &             61.5  &    1309 & 36492 \\
      280673 &            156.8  &    1453 & 33852 \\
      280862 &            137.8  &    1453 & 59833 \\
      281074 &             48.0  &    1596 & 36431 \\
      281143 &            210.2  &    1596 & 77801 \\
      281411 &            141.7  &    1813 & 46019 \\
      282992 &            112.1  &    1813 & 63457 \\
      283429 &            243.0  &    2029 & 73039 \\
      283780 &            151.3  &    2232 & 73218 \\
      284213 &            207.7  &    2232 & 77754 \\
      284285 &            255.8  &    2232 & 74323 \\
    \end{tabular}
    \caption{Data-taking conditions for runs used in the MDT/CSC hit rate studies. The integrated luminosity is taken from \href{https://atlas-lumicalc.cern.ch/results/b8e9b9/result.html}{lumicalc (b8e9b9)}.}
    \label{tab:zerobias}
  \end{center}
\end{table}


